Choose a License

### 2024-09-07 choose_license.qmd
Make data flowchart more explicit

  type --"Software"--> code_sa("Attribution?<br>State changes?<br>Copyleft?")
  type --"Writing, image, audio, video"--> nocode_cc("Anti-DRM?<br>Attribution?<br>State changes?<br>Copyleft?")

@@

  nocode_cc --"Neither"--> cc0["CC0 1.0"]
  nocode_cc --"Anti-DRM &<br>Attribution &<br>State changes"--> cc_by["CC BY 4.0"]
  nocode_cc --"Anti-DRM &<br>Attribution &<br>State changes &<br>Copyleft"--> cc_by_sa["CC BY-SA 4.0"]

@@

DRM = digital rights management

@@

  cc0_content_metadata --> cc0_db["CC0 1.0"]
  switch_license --"CC0 or<br>non-CC license"--> sa(Copyleft?)
  switch_license --"CC BY or<br>CC BY-SA"--> same["<em>Same license for DB</em>"]

  sa --"No (permissive)"--> cc0_db
  sa --"Yes"--> odbl["ODbL 1.0"]

>>>>

  type --"Software"--> code_sa("Attribution?<br>State changes?<br>Copyleft?")
  type --"Writing, image, audio, video"--> nocode_cc("Attribution?<br>State changes?<br>Anti-DRM?<br>Copyleft?")

@@

  nocode_cc --"Neither"--> cc0["CC0 1.0"]
  nocode_cc --"Attribution &<br>State changes &<br>Anti-DRM"--> cc_by["CC BY 4.0"]
  nocode_cc --"Attribution &<br>State changes &<br>Anti-DRM &<br>Copyleft"--> cc_by_sa["CC BY-SA 4.0"]

@@

Note: DRM = digital rights management

@@

  cc0_content_metadata --> cc0_db["CC0 1.0"]
  switch_license --"CC0 or<br>non-CC license"--> sa("Attribution?<br>Anti-DRM?<br>Copyleft?")
  switch_license --"CC BY or<br>CC BY-SA"--> same["<em>Same license for DB</em>"]

  sa --"Neither"--> cc0_db
  sa --"Attribution &<br>Anti-DRM &<br>Copyleft"--> odbl["ODbL 1.0"]
